Maenpuen et al.~Appendix S1-7: Sources and consequences of mismatch between leaf disc and whole-leaf leaf mass per area (LMA)

### 2022-04-07 ms/LMA_method.tex
udpate make

Phisamai Maenpuen\textsuperscript{1,2,3}, Masatoshi
Katabuchi\textsuperscript{1,*}, Yusuke Onoda\textsuperscript{4}, Cong
Zhou\textsuperscript{1,2}, Jiao-Lin Zhang\textsuperscript{1,3*}, Ya-Jun
Chen\textsuperscript{1,3,5}

@@

We used newly compiled individual-level plant datasets form a wide
ranges of biomes in China and Japan (Table S1) to examine the
relationship between whole-leaf and leaf disc-based estimates of leaf
traits. First, the Yunnan dataset is from three forest plots in Yunnan
province, Southwest China, which includes a tropical rain forest (TRF),
a hot-dry savanna ecosystem (HDS), and a subtropical evergreen wet
forest (STF), with a total of 141 species and 846 individuals. Second,
the Yakushima data is from a warm-temperate forest in Yakushima island,
Japan, with a total of 193 species and 519 individuals. In total, we
used 334 woody species and 1365 individuals. The methodologies for trait
sampling and measurement are slightly different between the Yunnan and
the Yakushima dataset, which we describe bellow.

@@

To determine what extent LMA values were affected by the different
methods, LMA were determined (i) LMA based on a whole leaf including
petioles and (ii) LMA based on leaf disc avoiding thick veins. Three
0.6-cm diameter discs were taken from the base, middle and tip of each
leaf using a hole punch in the Yunnan dataset. Two 1.0-cm diameter discs
were taken from each leaf were in the Yakushima dataset. Fresh leaf area
(LA; cm\textsuperscript{-2}) of leaf materials (whole leaves including
petioles and midribs) was measured using a scanner and ImageJ software
by the R package \emph{LeafArea}
(\protect\hyperlink{ref-Katabuchi2015}{Katabuchi, 2015}). Fresh leaf
thickness (LT; mm) was measured using a micrometer in three points at
the base, middle and tip of the leaf using a micrometer (Mitutoyo
293-240, Mitutoyo Corporation, Kawasaki, Japan) with a precision at
0.001 mm. Thickness of each leaf disc was also measured for the Yunnan
dataset but not for the Yakushima dataset, which enables us to estimate
whole-leaf and leaf disc leaf tissue density (LD; g
cm\textsuperscript{-3}) separately in the Yunnan dataset. Leaf dry mass
(whole leaves including petioles and midribs, and leaf discs) was
recorded after drying 80°C for over 48 h to constant weight using an
electronic scale (Mettler-Toledo MS204TS, Columbus, OH, U.S.A.) with a
precision at 0.0001 g. In the subset of Yakushima dataset, leaf lamina
and petiole dry mass were also determined separately (81 out of 193
species) to quantify leaf support costs. Dry mass for leaf discs were
recorded 2-3 discs together for each leaf. Based on those measurements
of whole-leaf and leaf disc samples, LMA (g m\textsuperscript{-2}) was
calculated as the ratio of leaf dry mass to fresh leaf area, and LD was
calculated as the ratio of LMA to LT. We do not present results of LD in
the main text, because differences between whole-leaf LD and leaf disc
LD only depends on the ratio between whole-leaf LMA and leaf disc LMA
and measurement errors of leaf thickness (Appendix S2).

@@

Bivariate trait relationships between disc-based and whole-leaf
log-transformed LMA were summarized with variance explained
(\emph{R\textsuperscript{2}}) based on Pearson correlations and with
standardized major axis (SMA) regressions
(\protect\hyperlink{ref-Warton2006}{Warton et al., 2006}) across all the
samples and different leaf area and thickness groups. Species and
individual groups were divided into four categories based on the medians
of leaf area and leaf thickness across all species and all individuals,
respectively: thin and small-leaved, thin and large-leaved, thick and
small-leaved, thick and large-leaved species (individuals). Median
values are as following: small-leaved species (LA \textless{} 29.5
cm\textsuperscript{2}), thin-leaved species (LT \textless{} 0.28 mm),
small-leaved individuals (LA \textless{} 34.7 cm\textsuperscript{2}),
and thin-leaved individuals (LT \textless{} 0.26 mm).

@@

Disc-based estimates of species mean LMA matched well whole-leaf
estimates (Table 1; \emph{R\textsuperscript{2}} = 0.87 for all species).
Species with thicker and smaller leaves had stronger correlations
between disc-based and whole-leaf estimates of LMA (Table 1, Fig. 1).
There was a negative correlation between species mean leaf area and leaf
thickness (\emph{r} = -0.29, \emph{P} \textless{} 0.05, \emph{n} = 334).
When we pooled all the species, there were significant differences in
intercepts for species mean LMA (Table 1), suggesting that the
whole-leaf estimates of LMA were 9.4\% greater than disc-based estimates
in the arithmetic scale. Large-leaved species also had significant
positive intercepts, suggesting that whole-leaf estimates of LMA were
22.1\% greater than disc-based estimates in the arithmetic scale (Table
1). Intercepts did not differ for small-leaved species (Table 1).

@@

Disc-based traits explained interspecific variations in whole-leaf LMA
(\emph{R\textsuperscript{2}} = 0.87, \emph{n} = 334) quite well, and the
strength of their relationship was approximately same or slightly weaker
than previously reported (\emph{R\textsuperscript{2}} = 0.92, \emph{n} =
409, for whole-leaves in Kraft et al.
(\protect\hyperlink{ref-Kraft2008}{2008}), \emph{R\textsuperscript{2}} =
0.92, \emph{n} = 364 for leaf laminas in Onoda et al.
(\protect\hyperlink{ref-Onoda2011}{2011})). Standardized major axis
(SMA) regression analysis showed significantly greater intercepts when
all the species were pooled (9.4\% differences) or large-leaved species
were used (22.1\% differences). Together, these findings suggest that
disc-based estimates can be generally used as good proxies for their
whole-leaf estimates with appropriate calibration. However, the strength
of correlations highly depended on leaf area, thickness (Fig. 1) and
sizes of leaf punches (Appendix S3 and S5).

@@

\includegraphics{../figs/LMA_sp_gr.png}

@@

\includegraphics{../figs/LMA_ind_gr.png}

@@

\includegraphics{../figs/fig_cv.png}

>>>>

Phisamai Maenpuen\textsuperscript{1,2,3}, Masatoshi
Katabuchi\textsuperscript{1*}, Yusuke Onoda\textsuperscript{4}, Cong
Zhou\textsuperscript{1,2}, Jiao-Lin Zhang\textsuperscript{1,3*}, Ya-Jun
Chen\textsuperscript{1,3,5}

@@

We used newly compiled individual-level plant datasets form a wide
ranges of biomes in China and Japan (Table S1) to examine the
relationship between whole-leaf and leaf disc-based estimates of leaf
traits. First, the Yunnan dataset is from three forest plots in Yunnan
province, Southwest China, which includes a tropical rain forest (TRF),
a hot-dry savanna ecosystem (HDS), and a subtropical evergreen wet
forest (STF), with a total of species and individuals. Second, the
Yakushima data is from a warm-temperate forest in Yakushima island,
Japan, with a total of 193 species and individuals. In total, we used
334 woody species and individuals. The methodologies for trait sampling
and measurement are slightly different between the Yunnan and the
Yakushima dataset, which we describe bellow.

@@

To determine what extent LMA values were affected by the different
methods, LMA were determined (i) LMA based on a whole leaf including
petioles and (ii) LMA based on leaf disc avoiding thick veins. Three
0.6-cm diameter discs were taken from the base, middle and tip of each
leaf using a hole punch in the Yunnan dataset. Two 1.0-cm diameter discs
were taken from each leaf were in the Yakushima dataset. Fresh leaf area
(LA; cm\textsuperscript{-2}) of leaf materials (whole leaves including
petioles and midribs) was measured using a scanner and ImageJ software
by the R package \emph{LeafArea}
(\protect\hyperlink{ref-Katabuchi2015}{Katabuchi, 2015}). Fresh leaf
thickness (LT; mm) was measured using a micrometer in three points at
the base, middle and tip of the leaf using a micrometer (Mitutoyo
293-240, Mitutoyo Corporation, Kawasaki, Japan) with a precision at
0.001 mm. Thickness of each leaf disc was also measured for the Yunnan
dataset but not for the Yakushima dataset, which enables us to estimate
whole-leaf and leaf disc leaf tissue density (LD; g
cm\textsuperscript{-3}) separately in the Yunnan dataset. Leaf dry mass
(whole leaves including petioles and midribs, and leaf discs) was
recorded after drying 80°C for over 48 h to constant weight using an
electronic scale (Mettler-Toledo MS204TS, Columbus, OH, U.S.A.) with a
precision at 0.0001 g. In the subset of Yakushima dataset, leaf lamina
and petiole dry mass were also determined separately (87 out of 193
species) to quantify leaf support costs. Dry mass for leaf discs were
recorded 2-3 discs together for each leaf. Based on those measurements
of whole-leaf and leaf disc samples, LMA (g m\textsuperscript{-2}) was
calculated as the ratio of leaf dry mass to fresh leaf area, and LD was
calculated as the ratio of LMA to LT. We do not present results of LD in
the main text, because differences between whole-leaf LD and leaf disc
LD only depends on the ratio between whole-leaf LMA and leaf disc LMA
and measurement errors of leaf thickness (Appendix S2).

@@

Bivariate trait relationships between disc-based and whole-leaf
log-transformed LMA were summarized with variance explained
(\emph{R\textsuperscript{2}}) based on Pearson correlations and with
standardized major axis (SMA) regressions
(\protect\hyperlink{ref-Warton2006}{Warton et al., 2006}) across all the
samples and different leaf area and thickness groups. Species and
individual groups were divided into four categories based on the medians
of leaf area and leaf thickness across all species and all individuals,
respectively: thin and small-leaved, thin and large-leaved, thick and
small-leaved, thick and large-leaved species (individuals). Median
values are as following: small-leaved species (LA \textless{}
cm\textsuperscript{2}), thin-leaved species (LT \textless{} mm),
small-leaved individuals (LA \textless{} cm\textsuperscript{2}), and
thin-leaved individuals (LT \textless{} mm).

@@

Disc-based estimates of species mean LMA matched well whole-leaf
estimates (Table 1; \emph{R\textsuperscript{2}} = for all species).
Species with thicker and smaller leaves had stronger correlations
between disc-based and whole-leaf estimates of LMA (Table 1, Fig. 1).
There was a negative correlation between species mean leaf area and leaf
thickness (\emph{r} = , \emph{P} , \emph{n} = ). When we pooled all the
species, there were significant differences in intercepts for species
mean LMA (Table 1), suggesting that the whole-leaf estimates of LMA were
9.4\% greater than disc-based estimates in the arithmetic scale.
Large-leaved species also had significant positive intercepts,
suggesting that whole-leaf estimates of LMA were 22.1\% greater than
disc-based estimates in the arithmetic scale (Table 1). Intercepts did
not differ for small-leaved species (Table 1).

@@

Disc-based traits explained interspecific variations in whole-leaf LMA
(\emph{R\textsuperscript{2}} = , \emph{n} = ) quite well, and the
strength of their relationship was approximately same or slightly weaker
than previously reported (\emph{R\textsuperscript{2}} = 0.92, \emph{n} =
409, for whole-leaves in Kraft et al.
(\protect\hyperlink{ref-Kraft2008}{2008}), \emph{R\textsuperscript{2}} =
0.92, \emph{n} = 364 for leaf laminas in Onoda et al.
(\protect\hyperlink{ref-Onoda2011}{2011})). Standardized major axis
(SMA) regression analysis showed significantly greater intercepts when
all the species were pooled (9.4\% differences) or large-leaved species
were used (22.1\% differences). Together, these findings suggest that
disc-based estimates can be generally used as good proxies for their
whole-leaf estimates with appropriate calibration. However, the strength
of correlations highly depended on leaf area, thickness (Fig. 1) and
sizes of leaf punches (Appendix S3 and S5).

@@

\includegraphics{../figs/lalt_pool_grid.png}

@@

\includegraphics{../figs/lalt_tree_grid.png}

@@

\includegraphics{../figs/cv_pool.png}
